### 2016-07-20 lineups.Rnw
added some explanation

>>>>

\begin{figure}
<<results0b, fig.width=8, fig.height=8, out.width='\\linewidth', echo = FALSE, warning = FALSE>>=
load("Data/lus_ests_truth.rda")
lus_ests_truth$param_name <- 
  factor(lus_ests_truth$param_name,
    levels = c("rate", "outdegree (density)", "reciprocity",
               "transitive triplets jumping alcohol2",
               "number pairs at doubly achieved distance 2"))        
lus_ests_truth$model_label <- lus_ests_truth$model
lus_ests_truth$true_model_label <- sprintf("True~Model:~%s", lus_ests_truth$true_model)
lus_ests_truth$param_label <- c("alpha", "beta[1]", "beta[2]", "beta[3]", "beta[4]")[as.numeric(lus_ests_truth$param_name)]
ggplot(data=lus_ests_truth %>% 
         filter(
           !is.na(convergence),
           (true_model=="M3" & model != "M2") | (true_model=="M1") |
             (true_model=="M2" & model != "M3")
           )) +
  geom_rect(xmin=-25, xmax=25, ymin=-0.5, ymax = 1, fill=rgb(.25,.25,.25,alpha=.25), data=unique(subset(lus_ests_truth, (true_model==model) & (!is.na(param_est)) )[,c("true_model_label", "model_label", "param_label")]) ) +
  geom_vline(xintercept = 0, colour="grey50") +
  geom_density(aes(x=param_est-true_value, fill=convergence), 
               alpha= 0.6) +
  facet_grid(model_label+param_label~true_model_label, drop=TRUE, labeller=label_parsed) +
  theme_bw() +
  theme(legend.position="bottom", 
        strip.text.y = element_text(angle=0)) + 
  scale_fill_brewer("Convergence", palette="Set1") +
  xlab("Difference between parameter estimate and true value") + 
    xlim(c(-15,15))
@
\caption{\label{fig:convergence-ests} Difference between parameter estimate and true value. 
Panels with a light grey background show model fits with data sampled from the same model.  Densities are drawn for both converged and non-converged data. The red-filled densities should have a mode in zero, indicating that the model converged in the correct value. For data from model $M_1$ estimates for parameters $\beta_3$ and $\beta_4$ converge to a wrong value.
}
\end{figure}
